Lawrence Bull, PhD

### 2024-12-17 index.qmd
bio update

Researcher Fellow [[Stats, UoG]](https://www.gla.ac.uk/schools/mathematicsstatistics/staff/lawrencebull/#biography) in machine learning for physical systems. Particularly tools to encode structure (via domain knowledge) into data-driven models. Statistical methods for telemetry data from machines and infrastructure.

>>>>

Research Fellow [[Stats, UoG]](https://www.gla.ac.uk/schools/mathematicsstatistics/staff/lawrencebull/#biography) in machine learning for physical systems. Particularly tools to encode structure (via domain knowledge) into data-driven models. Statistical methods for telemetry data from machines and infrastructure.
